Ecosystem size and complexity are extrinsic drivers of food chain length in branching networks

### 2022-10-31 rmd/manuscript.Rmd
Update manuscript.Rmd

$$
\begin{aligned}
A'_{i,x} &= s_{0,i}~\beta_{i,x}(t)~A_{i,x}(t)\\
\bar{A}_{i,x}(t) &= g_i(A'_{i,x})~A'_{i,x}~\gamma_{x}(t)
\end{aligned}
$$

@@

$$
\beta_{B,x}(t) = 1 - [z_{BC,x}(t) + z_{BP,x}(t)]
$$
where $z_{BC,x}(t)$ and $z_{BP,x}(t)$ are the proportional mortality of basal species caused by consumer and predator species, respectively. The total mortality is calculated as the proportion of total individuals consumed ($W_{B,x}(t)=W_{BC,x}(t) + \delta_{x}(t) W_{BP,x}(t)$) relative to the current abundance of the basal species ($A_{B,x}(t)$):

$$
z_{BC,x}(t) + z_{BP,x}(t) =\left\{\begin{aligned}&\frac{W_{BC,x}(t) + \delta_{x}(t) W_{BP,x}(t)}{A_{B,x}(t)} &&\text{if $W_{B,x}(t) < A_{B,x}(t)$}\\&1 &&\text{if $W_{B,x}(t) > A_{B,x}(t)$}\\\end{aligned}\right.
$$

where $W_{ij,x}(t)$ is the population-wide consumption of consumer $j$ on prey $i$ (number of individuals), and the parameter $\delta_{x}(t)$ is the relative preference of predator to basal species over consumer. We assume the Holling Type-II functional response for predator-prey interactions:

@@

$$
g_B(A'_{B,x}) = \frac{r_{b}} {1 + \frac{r_b - 1}{K_{x}}A_{B,x}'}
$$

@@

$$
g_C(A'_{C,x}) =
\left\{
\begin{aligned}
&e_{BC}W_{BC,x}(t) &&\text{if $W_{B,x}(t) < A_{B,x}(t)$}\\
&e_{BC} \left( \frac{W_{BC,x}(t)}{W_{B,x}(t)} A_{B,x} \right) &&\text{if $W_{B,x}(t) > A_{B,x}(t)$}\\\end{aligned}\right.
$$

@@

$$
g_P(A'_{P,x}) =
\left\{
\begin{aligned}
&e_{BP} \delta_{x}(t) W_{BP,x}(t) + e_{CP} (1 - \delta_{x}(t)) W_{CP,x}(t) &&\text{if $W_{B,x}(t) < A_{B,x}(t)$}\\
&e_{BP} \delta_{x}(t)\left(\frac{W_{BP,x}(t)}{W_{B,x}(t)}A_{B,x}\right) + e_{CP} (1 - \delta_{x}(t)) W_{CP,x}(t) &&\text{if $W_{B,x}(t) > A_{B,x}(t)$}\\
\end{aligned}
\right.
$$

>>>>

$$
\begin{aligned}
A'_{i,x} &= s_{0,i}~\beta_{i,x}(t)~A_{i,x}(t)\\
\bar{A}_{i,x}(t) &= g_i(A)~A'_{i,x}~\gamma_{x}(t)
\end{aligned}
$$

@@

$$
\beta_{B,x}(t) = 1 - [z_{BC,x}(t) + z_{BP,x}(t)]
$$
where $z_{BC,x}(t)$ and $z_{BP,x}(t)$ are the proportional mortality of basal species caused by consumer and predator species, respectively. The total mortality is calculated as the proportion of total individuals consumed ($W_{B,x}(t)$) relative to the current abundance of the basal species ($A_{B,x}(t)$):

$$
z_{BC,x}(t) + z_{BP,x}(t) =
\left\{
\begin{aligned}
&\frac{W_{B,x}(t)}{A_{B,x}(t)} &&\text{if $W_{B,x}(t) < A_{B,x}(t)$}\\
&1 &&\text{if $W_{B,x}(t) > A_{B,x}(t)$}\\
\end{aligned}
\right.
$$

where

$$
W_{B,x}(t)=W_{BC,x}(t) + \delta_{x}(t) W_{BP,x}(t)
$$\
$W_{ij,x}(t)$ is the population-wide consumption of consumer $j$ on prey $i$ (number of individuals), and the parameter $\delta_{x}(t)$ is the relative preference of predator to basal species over consumer. We assume the Holling Type-II functional response for predator-prey interactions:

@@

$$
g_B(A) = \frac{r_{b}} {1 + \frac{r_b - 1}{K_{x}}A_{B,x}'}
$$

@@

$$
g_C(A) =
\left\{
\begin{aligned}
&e_{BC}W_{BC,x}(t) &&\text{if $W_{B,x}(t) < A_{B,x}(t)$}\\
&e_{BC} \left( \frac{W_{BC,x}(t)}{W_{B,x}(t)} A_{B,x}(t) \right) &&\text{if $W_{B,x}(t) > A_{B,x}(t)$}\\\end{aligned}\right.
$$

@@

$$
g_P(A) =
\left\{
\begin{aligned}
&e_{BP} \delta_{x}(t) W_{BP,x}(t) + e_{CP} (1 - \delta_{x}(t)) W_{CP,x}(t) &&\text{if $W_{B,x}(t) < A_{B,x}(t)$}\\
&e_{BP} \delta_{x}(t)\left(\frac{W_{BP,x}(t)}{W_{B,x}(t)}A_{B,x}\right) + e_{CP} (1 - \delta_{x}(t)) W_{CP,x}(t) &&\text{if $W_{B,x}(t) > A_{B,x}(t)$}\\
\end{aligned}
\right.
$$
